HO unification from object language to meta language

### 2024-02-14 main.tex
tex

\begin{coqcode}
(* HO unif *)
Instance forall_dec A (P: A |$\to$| Prop) `{Finite A} `{|$\forall$|x, Decision (P x)} :
  Decision (|$\forall$|x, P x).
Instance and_dec P `{Decision P} Q `{Decision Q}:  Decision (P ∧ Q).

@@

\end{coqcode}

@@

\begin{elpicode}
  kind fo_tm type.
  type fo_app list fo_tm -> fo_tm.
  type fo_lam (tm -> fo_tm) -> fo_tm.
  type fo_uv  nat -> fo_tm.
  type fo_c string -> fo_tm.
\end{elpicode}

\begin{elpicode}
  kind tm type.
type app list tm -> tm.
type lam (tm -> tm) -> tm.
type uv  nat -> list tm -> tm.
type c string -> tm.
\end{elpicode}

@@

\begin{elpicode}
  p (all x\ app[F,x]) = p (all x\ app[f,x,x])
\end{elpicode}

@@

\begin{elpicode}
  p (all x\ F' x) = p (all x\ app[f,x,x]) , link F F'.
  F' = x\ app[f,x,x]
  F = lam a\ app[f,a,a].
\end{elpicode}

\begin{elpicode}
  type comp fo.tm -> ho.tm -> list link -> list link -> ho.subst -> ho.subst -> o.
  comp (fo.c X)   (ho.c X) L L S S.
  comp (fo.app [fo.uv N|Argsss]) TT L L3 S S3 :- %!,
    % TODO: here split-pf to enter dist. names into N
    % split-pf Argsss [] PF NPF,
    split-pf Argsss [] PF [], NPF = [], % TODO: compile to (uv N L) + link-fo-app
    print "In PF" PF NPF, 
    if (NPF = []) (TT = ho.uv M PF1) (TT = ho.app [ho.uv M PF1 | NPF1]),
    % pattern-fragment Args,
    fold4 comp PF PF1 L L1 S S1,
    fold4 comp NPF NPF1 L1 L2 S1 S2,
    ho.new S2 M S3,
    % TODO: maybe len can be given by split-pf
    len PF Len,
    L3 = [link N M Len| L2].
  % TODO: if don't want to modify unif, we compile `fo.app [fo.c f, c0, c0, ho.c a]` into 
  % `ho.app [ho.app[f, c0, c0], ho.c a]
  comp (fo.app A) (ho.app A1) L L1 S S1 :- fold4 comp A A1 L L1 S S1.
  comp (fo.lam F) (ho.lam F1) L L1 S S1 :- 
    (pi x y\ (pi A S\ comp x y A A S S) => comp (F x) (F1 y) L L1 S S1).
  comp (fo.uv N) (ho.uv M []) L [link N M z|L] S S1 :- ho.new S M S1.

  decmop...
\end{elpicode}

@@

\begin{elpicode}
q (all x\ F x) = q (all x\ app[f,x]) /\ p f = p F
F = fun a => app [f,a] ----> F = f
\end{elpicode}

@@

\begin{elpicode}
  q (all x\ F x) = q (all x\ app[f,x,x]) /\ p1 (app[f,a,a]) = p1 (app[F,a])
  F = fun y => app [f,y,y] ----> (app[F,a]) ~> app[f, a, a].
\end{elpicode}

@@

\begin{elpicode}
  q2 (all x\ F x) (app[F,a]) = q2 (all x\ app[f,x,x]) (app[f,a,a])
\end{elpicode}

@@

\begin{elpicode}
  p (all x\app[F,x,a]) (app[F,b]) = p (all x\app[f,x,x,a]) (app[f,b,b])
  p (all x\G x) F' = 
  G = x\ f x x a
  F = lam x\f x x
  F' = (app[f,b,b])
  link (F a) F'
  link G F
\end{elpicode}

questo esempio recupera l'app binaria perche

\begin{elpicode}
  (app (app F x) a) = (app (f x x) a)
\end{elpicode}

>>>>

\begin{minted}[escapeinside=||,mathescape=true]{coq}
(* HO unif *)
Instance forall_dec A (P: A |$\to$| Prop) `{Finite A} `{|$\forall$|x, Decision (P x)} :
  Decision (|$\forall$|x, P x).
Instance and_dec P `{Decision P} Q `{Decision Q}:  Decision (P /\ Q).

@@

\end{minted}

@@

\begin{minted}{elpi}
  kind fo_tm type.
  type fo_app list fo_tm -> fo_tm.
  type fo_lam (tm -> fo_tm) -> fo_tm.
  type fo_uv  nat -> fo_tm.
  type fo_c string -> fo_tm.
\end{minted}

\begin{minted}{elpi}
  kind tm type.
type app list tm -> tm.
type lam (tm -> tm) -> tm.
type uv  nat -> list tm -> tm.
type c string -> tm.
\end{minted}

@@

\begin{minted}{elpi}
  p (all x\ app[F,x]) = p (all x\ app[f,x,x])
\end{minted}

@@

\begin{minted}{elpi}
  p (all x\ F' x) = p (all x\ app[f,x,x]) , link F F'.
  F' = x\ app[f,x,x]
  F = lam a\ app[f,a,a].
\end{minted}

\begin{minted}{elpi}
  type comp fo.tm -> ho.tm -> list link -> list link -> ho.subst -> ho.subst -> o.
  comp (fo.c X)   (ho.c X) L L S S.
  comp (fo.app [fo.uv N|Argsss]) TT L L3 S S3 :- %!,
    % TODO: here split-pf to enter dist. names into N
    % split-pf Argsss [] PF NPF,
    split-pf Argsss [] PF [], NPF = [], % TODO: compile to (uv N L) + link-fo-app
    print "In PF" PF NPF, 
    if (NPF = []) (TT = ho.uv M PF1) (TT = ho.app [ho.uv M PF1 | NPF1]),
    % pattern-fragment Args,
    fold4 comp PF PF1 L L1 S S1,
    fold4 comp NPF NPF1 L1 L2 S1 S2,
    ho.new S2 M S3,
    % TODO: maybe len can be given by split-pf
    len PF Len,
    L3 = [link N M Len| L2].
  % TODO: if don't want to modify unif, we compile `fo.app [fo.c f, c0, c0, ho.c a]` into 
  % `ho.app [ho.app[f, c0, c0], ho.c a]
  comp (fo.app A) (ho.app A1) L L1 S S1 :- fold4 comp A A1 L L1 S S1.
  comp (fo.lam F) (ho.lam F1) L L1 S S1 :- 
    (pi x y\ (pi A S\ comp x y A A S S) => comp (F x) (F1 y) L L1 S S1).
  comp (fo.uv N) (ho.uv M []) L [link N M z|L] S S1 :- ho.new S M S1.

  decmop...
\end{minted}

@@

\begin{minted}{elpi}
q (all x\ F x) = q (all x\ app[f,x]) /\ p f = p F
F = fun a => app [f,a] ----> F = f
\end{minted}

@@

\begin{minted}{elpi}
  q (all x\ F x) = q (all x\ app[f,x,x]) /\ p1 (app[f,a,a]) = p1 (app[F,a])
  F = fun y => app [f,y,y] ----> (app[F,a]) ~> app[f, a, a].
\end{minted}

@@

\begin{minted}{elpi}
  q2 (all x\ F x) (app[F,a]) = q2 (all x\ app[f,x,x]) (app[f,a,a])
\end{minted}

@@

\begin{minted}{elpi}
  p (all x\app[F,x,a]) (app[F,b]) = p (all x\app[f,x,x,a]) (app[f,b,b])
  p (all x\G x) F' = 
  G = x\ f x x a
  F = lam x\f x x
  F' = (app[f,b,b])
  link (F a) F'
  link G F
\end{minted}

% questo esempio recupera l'app binaria perche

\begin{minted}{elpi}
  (app (app F x) a) = (app (f x x) a)
\end{minted}
